### 2019-04-23 Appendices/AppendixE.tex
add ground state energy

An orthonormal basis for the extended Hilbert space can be obtained as the direct product an orthonormal basis of $\mathcal{H}$ and $\mathcal{L}_T$. A convenient orthonormal basis for $\mathcal{L}_T$ is given by the functions $e^{im\omega t}$, therefore, if $\ket{\alpha}$ labels an orthonormal basis of $\mathcal{H}$, then the set of functions $\ket{\alpha m (t)} = \ket{\alpha}e^{im\omega t}$ is a basis of the extended Floquet space, and it is denoted as $\ket{\alpha m}\rangle$. In this basis, the quasienergy operator has matrix elements:

@@

>>>>

An orthonormal basis for the extended Hilbert space can be obtained as the direct product of an orthonormal basis of $\mathcal{H}$ and $\mathcal{L}_T$. A convenient orthonormal basis for $\mathcal{L}_T$ is given by the functions $e^{im\omega t}$, where $m$ is usually referred to as the photon number. Then, if $\ket{\alpha}$ labels an orthonormal basis of $\mathcal{H}$, then the set of functions $\ket{\alpha m (t)} = \ket{\alpha}e^{im\omega t}$ is a basis of the extended Floquet space, and it is denoted as $\ket{\alpha m}\rangle$. In this basis, the quasienergy operator has matrix elements:

@@

\section{Diagonalization}

We introduce a unitary transformation $\hat{U}(t)=\sum_m e^{im\omega t}\hat{U}_m$, $\hat{Q} \rightarrow \hat{Q}'=\hat{U}^{\dagger}(t)\hat{Q}\hat{U}(t)$ or:

\begin{align}
\hat{H}(t) \rightarrow \hat{H}'(t) &= \hat{U}^{\dagger}(t)\hat{H}(t)\hat{U}(t) - i\hat{U}^{\dagger}(t)\text{d}_t\hat{U}(t) \\
\ket{\psi(t)} \rightarrow \ket{\psi'(t)} &= \hat{U}^{\dagger}(t)\ket{\psi(t)}
\end{align}

The goal is to find $\hat{U}(t)$ such that the transformed quasienergy operator $\hat{Q}'$ is block diagonal in the photon number. Using \ref{QOmatelem} we notice that this requirement is equivalent to the requirement that the transformed Hamiltonian $\hat{H}'(t)$ is time independent.

### 2019-04-23 Chapters/Chapter5.tex
add ground state energy

\begin{equation}
\hat{H} = J \sum_{\langle i j \rangle} \bs{S}_i \bs{S}_j
\end{equation}

@@

Where the sum is over $\bs{k}$ in the first Brillouin zone. Using these relations, together with $\sum{i} e^{i(\bs{k}-\bs{k}')\cdot\bs{r}_i} = \delta_{\bs{k}, \bs{k}'}$ we find:

\begin{equation}
\hat{H} = 2JS \sum_{\bs{k} \bs{\delta}} \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{\bs{k}}\hat{b}_{\bs{k}} + e^{i\bs{k}\bs{\delta}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + e^{-i \bs{k}\cdot\bs{\delta}}  \hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right)
\end{equation}

@@

\begin{equation}
\label{MagnonicH}
\hat{H} = 2JS \sum_{\bs{k}} \left\{ z \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
\end{equation}

@@

Acting on the spinor $\Psi_{\bs{k}} = \left(\hat{a}_{\bs{k}},\hat{b}_{-\bs{k}}^\dagger \right)^T$. That is, $\hat{H} = \sum_{\bs{k}} \Psi_{\bs{k}} \hat{H}_{\bs{k}} \Psi^\dagger_{\bs{k}}$. In order to diagonalize this Hamiltonian we introduce the Bogoliubov transformation:

@@

\begin{align}
\hat{H} &= 2JS \sum_{\bs{k}} \left\{ \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \left( z(\abs{u_{\bs{k}}}^2+\abs{v_{\bs{k}}}^2) -\gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^* - \gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) + \right. \nonumber \\
&+ \left.  \hat{\alpha}^\dagger_{\bs{k}} \hat{\beta}_{\bs{k}} \left( -2zu_{\bs{k}}v_{\bs{k}}^* + \gamma_{\bs{k}}(v_{\bs{k}}^*)^2+\gamma_{-\bs{k}}u_{\bs{k}}^2 \right) + \hat{\beta}_{\bs{k}}^\dagger\hat{\alpha}_{\bs{k}} \left( -2zu_{\bs{k}}^*v_{\bs{k}} + \gamma_{\bs{k}}(u_{\bs{k}}^*)^2+\gamma_{-\bs{k}}v_{\bs{k}}^2 \right) \right\} \label{BeforeBogo}
\end{align}

@@

\begin{align*}
u_{\bs{k}} &= \cosh(\frac{\theta_{\bs{k}}}{2})e^{i \xi_{\bs{k}}} \\
v_{\bs{k}} &= \sinh(\frac{\theta_{\bs{k}}}{2})
\end{align*}

@@

This erases the non diagonal terms in \ref{BeforeBogo} leading to a diagonal term:
\begin{equation}
z\cosh(\theta_{\bs{k}})-\abs{\gamma_{\bs{k}}}\sinh(\theta_{\bs{k}}) = \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2}
\end{equation}

Then, the dispersion relation is:

\begin{align}
\hat{H} &= \sum_{\bs{k}}\left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \epsilon_{\bs{k}} \\
\epsilon_{\bs{k}} &= 2JS \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2}
\end{align}

@@

\begin{equation}
D \sum_{\langle \langle i j \rangle \rangle} \nu_{ij}\hat{e}_z \bs{S}_i \times \bs{S}_j = 2JS\sum_{\bs{k}} \left\{ \Delta_{\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} - \Delta_{-\bs{k}}\hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right\}
\end{equation}

Where $\Delta_{\bs{k}} = \frac{Di}{2J}\sum_{\bs{\delta}^{NNN}} \nu_{i,i+\delta} (e^{i\bs{k}\cdot\bs{\delta}} -e^{-i\bs{k}\cdot\bs{\delta}})$, for $i$ in the $A$ sublattice. This can be rewritten as:
\begin{equation}
\Delta_{\bs{k}} = -\frac{2D}{J}\left\{ \sin(\bs{\delta}^{NNN}_1 \cdot \bs{k}) + \sin(\bs{\delta}^{NNN}_2 \cdot \bs{k}) + \sin(\bs{\delta}^{NNN}_3 \cdot \bs{k})\right\}
\end{equation}
The full magnonic Hamiltonian now is:

\begin{equation}
\label{MagnonicH2}
\hat{H} = 2JS \sum_{\bs{k}} \left\{ \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}}(z+\Delta_{\bs{k}}) + \hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}}(z-\Delta_{-\bs{k}}) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
\end{equation}

@@

\begin{equation}
\hat{H}_{\bs{k}} = 2JS\begin{pmatrix} 
z + \Delta_{\bs{k}}& \gamma_{\bs{k}} \\
\gamma_{-\bs{k}} & z - \Delta_{-\bs{k}}
\end{pmatrix}
\end{equation}

In this case, applying the transformation \ref{Bogoliubov} leads to the same condition for the coefficients  $u_{\bs{k}}$ and $v_{\bs{k}}$, whereas the energy gets lifted:

\begin{align}
\hat{H} &= \sum_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \epsilon_{\bs{k}}^+ +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}  \epsilon_{\bs{k}}^- \right) \label{DispWithDMI} \\
\epsilon_{\bs{k}}^\pm &= 2JS \left( \pm \Delta_{\bs{k}} + \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2} \right)
\end{align}

@@

\begin{figure}
\centering
  \includegraphics[width=0.7\linewidth]{../Figures/magnon_disp_2.png}
  \caption{The energy $\frac{\epsilon_{\bs{k}}^\pm}{JS}$ obtained for $D=0.1J$ }
\label{Fig.Magnon.Disp}
\end{figure}

@@

Let's now introduce a term:

@@

Where $\Delta'_{\bs{k}} = \sum_{\delta^{NNN}} \left( e^{i\bs{k}\cdot \bs{\delta}^{NNN}} +  e^{-i\bs{k}\cdot \bs{\delta}^{NNN}}\right) = 4\left\{ \cos(\delta^{NNN}_1\cdot\bs{k}) + \cos(\delta^{NNN}_2\cdot\bs{k}) + \cos(\delta^{NNN}_3\cdot\bs{k})\right\}$ and $\tilde{\Gamma}_{\bs{k}} = \frac{1}{2J}\left( \Gamma_{xy}\Delta'_{\bs{k}}-4z\Gamma_z \right)$. Therefore, now:

@@

We obtain the dispersion relation by changing $z \rightarrow z + \tilde{\Gamma}_{\bs{k}}$ in \ref{DispWithDMI}:

\begin{align}
\hat{H} &= \sum_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \epsilon_{\bs{k}}^+ +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}  \epsilon_{\bs{k}}^- \right) \label{DispWithDMI} \\
\epsilon_{\bs{k}}^\pm &= 2JS \left( \pm \Delta_{\bs{k}} +  \sqrt{(z + \tilde{\Gamma}_{\bs{k}})^2-\abs{\gamma_{\bs{k}}}^2} \right)
\end{align}

>>>>

\begin{equation}
\label{Heisenberg}
\hat{H} = J \sum_{\langle i j \rangle} \bs{S}_i \bs{S}_j
\end{equation}

@@

Where the sum is over $\bs{k}$ in the first Brillouin zone. Using these relations, together with $\sum{i} e^{i(\bs{k}-\bs{k}')\cdot\bs{r}_i} = \delta_{\bs{k}, \bs{k}'}$ and denoting the number of sites by $N$ and the number of nearest neighbors by $z$, we find:

\begin{equation}
\hat{H} = -S^2JNz + 2JS \sum_{\bs{k} \bs{\delta}} \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{\bs{k}}\hat{b}_{\bs{k}} + e^{i\bs{k}\bs{\delta}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + e^{-i \bs{k}\cdot\bs{\delta}}  \hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right)
\end{equation}

@@

\begin{equation}
\label{MagnonicH}
\hat{H} = -S^2JNz + 2JS \sum_{\bs{k}} \left\{ z \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
\end{equation}

@@

Acting on the spinor $\Psi_{\bs{k}} = \left(\hat{a}_{\bs{k}},\hat{b}_{-\bs{k}}^\dagger \right)^T$. That is, $\hat{H} = -S^2JNz + \sum_{\bs{k}} \Psi_{\bs{k}} \hat{H}_{\bs{k}} \Psi^\dagger_{\bs{k}}$. In order to diagonalize this Hamiltonian we introduce the Bogoliubov transformation:

@@

\begin{align}
\hat{H} &= -S^2JNz + 2JS \sum_{\bs{k}} \left\{ \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \left( z(\abs{u_{\bs{k}}}^2+\abs{v_{\bs{k}}}^2) -\gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^* - \gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) + \right. \nonumber \\
&+ \hat{\alpha}^\dagger_{\bs{k}} \hat{\beta}^\dagger_{\bs{k}} \left( -2zu_{\bs{k}}v_{\bs{k}}^* + \gamma_{\bs{k}}(v_{\bs{k}}^*)^2+\gamma_{-\bs{k}}u_{\bs{k}}^2 \right) + \hat{\alpha}_{\bs{k}}\hat{\beta}_{\bs{k}} \left( -2zu_{\bs{k}}^*v_{\bs{k}} + \gamma_{\bs{k}}(u_{\bs{k}}^*)^2+\gamma_{-\bs{k}}v_{\bs{k}}^2 \right) + \nonumber \\
&\left. + \left( 2z\abs{v_{\bs{k}}}^2 - \gamma_{\bs{k}}u_{\bs{k}}^* v_{\bs{k}}^* - \gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) \right\} \label{AfterBogo}
\end{align}

@@

\begin{align}
u_{\bs{k}} &= \cosh(\frac{\theta_{\bs{k}}}{2})e^{i \xi_{\bs{k}}} \label{Bogou} \\
v_{\bs{k}} &= \sinh(\frac{\theta_{\bs{k}}}{2}) \label{Bogov}
\end{align}

@@

This erases the non diagonal terms in \ref{AfterBogo} leading to a diagonal term:
\begin{equation}
z\cosh(\theta_{\bs{k}})-\abs{\gamma_{\bs{k}}}\sinh(\theta_{\bs{k}}) = \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2}
\end{equation}

With this, we can rewrite \ref{AfterBogo} as:

\begin{align}
\hat{H} &= -S^2JNz + 2JS \sum_{\bs{k}}\left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}+1 \right)\epsilon_{\bs{k}}+2JS \sum_{\bs{k}}z(\abs{v_{\bs{k}}}^2-\abs{u_{\bs{k}}}^2) = \nonumber \\
&= E_0 + \sum_{\bs{k}}\left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right)
\end{align}

Where we used $\sum_{\bs{k}}=\frac{N}{2}$ and where $\epsilon_{\bs{k}} = 2JS \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2}$. The ground state energy of this magnon Hamiltonian is:
\begin{equation}
E_0 = -JNz(S^2+S)+\sum_{\bs{k}}\epsilon_{\bs{k}} \label{HeisenbergMagnonGS}
\end{equation}
Note that the classical ground energy of \ref{Heisenberg} is $E_{cl}=-JNzS^2$, whereas the ground state that we obtained is lowered by:
\begin{equation}
\Delta E=-JNzS+\sum_{\bs{k}}\epsilon_{\bs{k}} = 2JS\sum_{\bs{k}}\left( \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2} - z\right)
\end{equation}
Which is indeed negative since the terms in the sum are always negative. This term represents quantum corrections to the classical ground energy $E_{cl}$. Note that the fact that the quantum corrections lower the energy of the classical ground state means that the classical ground state (N\'eel order) is not an eigenstate of the Heisenberg Hamiltonian.

@@

\begin{equation}
D \sum_{\langle \langle i j \rangle \rangle} \nu_{ij}\hat{e}_z \bs{S}_i \times \bs{S}_j = 2JS\sum_{\bs{k}} \left\{ \Delta_{\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \Delta_{-\bs{k}}\hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right\}
\end{equation}

Where $\Delta_{\bs{k}} = \frac{Di}{2J}\sum_{\bs{\delta}^{NNN}} \nu_{i,i+\delta} (e^{i\bs{k}\cdot\bs{\delta}} -e^{-i\bs{k}\cdot\bs{\delta}})$, for $i$ in the $A$ sublattice. This can be rewritten as:
\begin{equation}
\Delta_{\bs{k}} = -\frac{2D}{J}\left\{ \sin(\bs{\delta}^{NNN}_1 \cdot \bs{k}) + \sin(\bs{\delta}^{NNN}_2 \cdot \bs{k}) + \sin(\bs{\delta}^{NNN}_3 \cdot \bs{k})\right\}
\end{equation}

Note that $\Delta_{\bs{k}}=-\Delta_{-\bs{k}}$ .The full magnonic Hamiltonian now is:

\begin{equation}
\label{MagnonicH2}
\hat{H} = -S^2JNz + 2JS \sum_{\bs{k}} \left\{ \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}}(z+\Delta_{\bs{k}}) + \hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}}(z-\Delta_{\bs{k}}) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
\end{equation}

@@

\begin{equation}
\hat{H}_{\bs{k}} = 2JS\begin{pmatrix} 
z + \Delta_{\bs{k}}& \gamma_{\bs{k}} \\
\gamma_{-\bs{k}} & z - \Delta_{\bs{k}}
\end{pmatrix} \label{MatrixMagnonDMI}
\end{equation}

In this case, applying the transformation \ref{Bogoliubov} leads to the same condition for the coefficients  $u_{\bs{k}}$ and $v_{\bs{k}}$, leading to:

\begin{align*}
\hat{H} &= -S^2JNz  + 2JS\sum_{\bs{k}} \left\{ \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \left( \abs{u_{\bs{k}}}^2(z+\Delta_{\bs{k}}) + \abs{v_{\bs{k}}}^2(z-\Delta_{\bs{k}}) -\gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^*-\gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) + \right. \\
&\left. + \hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \left( \abs{u_{\bs{k}}}^2(z-\Delta_{\bs{k}}) + \abs{v_{\bs{k}}}^2(z+\Delta_{\bs{k}}) -\gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^*-\gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) + \right. \\
&\left. + \left( 2\abs{v_{\bs{k}}}^2 - \gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^*-\gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}}\right) \right\}
\end{align*}

Where we already took \ref{Bogou} and \ref{Bogov}. The ground state energy $E_0$ remains the same as in the base Heisenberg model while the excitation modes $\hat{\alpha}_{\bs{k}}^\dagger$ and $\hat{\beta}_{\bs{k}}^\dagger$ change in the following way:

\begin{align}
\hat{H} &= E_0 + \sum_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \epsilon_{\bs{k}}^+ +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}  \epsilon_{\bs{k}}^- \right) \label{DispWithDMI} \\
\epsilon_{\bs{k}}^\pm &= 2JS \left( \pm \Delta_{\bs{k}} + \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2} \right)
\end{align}

@@

\begin{figure}
\centering
  \includegraphics[width=0.7\linewidth]{../Figures/magnon_disp_2.png}
  \caption{The energy $\frac{\epsilon_{\bs{k}}^\pm}{JS}$ obtained for $D=0.1J$. For simplicity we take $E_0 = 0$. }
\label{Fig.Magnon.Disp}
\end{figure}

@@

We would like to see how the anisotropic spin interaction derived in \ref{MKMHeff} enters in the magnon Hamiltonian. To this end, we introduce now a term:

@@

Where we defined:
\begin{align*}
\Delta'_{\bs{k}} &= \sum_{\delta^{NNN}} \left( e^{i\bs{k}\cdot \bs{\delta}^{NNN}} +  e^{-i\bs{k}\cdot \bs{\delta}^{NNN}}\right) = 4\left\{ \cos(\delta^{NNN}_1\cdot\bs{k}) + \cos(\delta^{NNN}_2\cdot\bs{k}) + \cos(\delta^{NNN}_3\cdot\bs{k})\right\} \\
\tilde{\Gamma}_{\bs{k}} &= \frac{1}{2J}\left( \Gamma_{xy}\Delta'_{\bs{k}}-4z\Gamma_z \right)
\end{align*}
Therefore, now:

@@

This is the same as \ref{MatrixMagnonDMI} if we replace $z \rightarrow z + \tilde{\Gamma}_{\bs{k}}$, therefore the magnon Hamiltonian is:

\begin{align}
\hat{H} &= E_0 + \sum_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \epsilon_{\bs{k}}^+ +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}  \epsilon_{\bs{k}}^- \right) \\
\epsilon_{\bs{k}}^\pm &= 2JS \left( \pm \Delta_{\bs{k}} +  \sqrt{(z + \tilde{\Gamma}_{\bs{k}})^2-\abs{\gamma_{\bs{k}}}^2} \right)
\end{align}

This concludes our discussion of the magnons in the models derived in the last Chapter. The main difference of the magnonic Hamiltonian of a Kane-Mele system with a simple Heisenberg interaction is that the $\hat{\alpha}_{\bs{k}}^\dagger$ and $\hat{\beta}_{\bs{k}}^\dagger$ modes have non degenerate spectrum. This is arising from the addition of DMI in the model which breaks the symmetry of the system.
